---
title: "langley1_OriginalHomeworkCode_02"
output: html_document
---
***

# **Homework 2: Titis in the Mist**

***

This is my code for [Homework 2](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html)

> Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

We want to use the Poisson Distribution because it is often used to model open ended counts of independently occuring events, i.e the number of times a monkey calls in a given interval

The Poisson distribution function, ppois(), returns the value of the cumulative distribution function, i.e., the probability of observing up to and including a specific number of events in the given interval (so this relates to the question)

## Question 1 

What is the probability that she will hear more than 8 calls during any given session?
```{r}
#We know that the mean number of calls is 15, so lambda= 15
#We know that the number of successes should be >8 but we can't put "9:infinity" for our q value... but we can find the probability for 0:8 and then take the inverse of that for >8... lets try it!

q<- 0:8
l<- 15
prob1.2<- ppois(q, l, lower.tail = TRUE, log.p = FALSE)
prob1.2 #3.059023e-07 4.894437e-06 3.930845e-05 2.113785e-04 8.566412e-04 2.792429e-03 7.631900e-03 1.800219e-02 3.744649e-02

#If these numbes above are showing me all of the probabilities for the range of 0 - 8 calls, then I'm going to add them up and take the inverse of that number
ProbSum<- sum(prob1.2) #0.067
CallsProb<- 1 - ProbSum
CallsProb #The probability she will hear more than 8 calls = 0.933

#Overall, I have absolutely no idea if this is right. This probability seems too high to me. 
```
 
## Question 2

### 2) What is the probability that she will hear no calls in a session?
```{r}
#Now we need to adjust our q value to 0 but we can keep lamda at 15
x<- 0
l<- 15
prob2<- dpois(x, l)
prob2 
```

## Question 3

### 3) What is the probability that she will hear exactly 3 calls in a session?
```{r}
#Now we can change our q value to equal 3 (note: the q value doesn't always need to be a range of numbers i.e. 0:100)
q<- 3
l<- 15
prob3<- ppois(q, lambda = l)
prob3 
```

## Question 4

### 4) Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
```{r}
x <- 0:30
l = 15
prob4<- dpois(x=x,lambda=l)
barplot(prob4,names.arg=x,space=0,xlab="Number of Calls",ylab="Probaility",main="Probability Mass Function")
```

## Question 5

### 5) Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
```{r}
#For simulations, we want to use Bootstrapping, 
#x <- 0:30
#l = 15
#set<- NULL #This is setting up a dummy variable to hold our 104 simulations
#for (i in 1:104){
   # set[i] <- ppois(q=x,lambda = l)
#}
#This does not work!!! It returns a very crazy, long error (which you see if you knit this so I'm putting putting it as non-code for now), I have no idea how to set up the bootstrapping to make this work. So I did some research and came across rpois() for simulations, hopefully this one works better

sim<- rpois(104, lambda = 15)
sim #Yes this works much better 

```

## Question 6

### 6) Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?
```{r}
plot<- hist(sim, xlim = c(0,30), xlab = "Calls over 104 simulations", main = "Histogram")

#This histogram is pretty similar to the barplot using dpois(). They both have the highest probability/frequency around 14 calls with a range of ~5-28. The probability mass function plot is more evenly distributed across the range where the histogram is not and even has a break at 25 calls having 0 frequency.
```

## CHALLENGES

1. I still don't fully understand the difference between ppois() and dpois() and when to use them appropriately. 
2. For Question #1, I tried both "lower.tail= TRUE" and "lower.tail = FALSE", but the equation with "lower.tail = FALSE" gave me probabilities of ~0.99, which seemed way too high to me so I went with  "lower.tail = TRUE". However, I don't understand the difference between the two and when to use each one.
[lower.tail = logical; if TRUE (default), probabilities are P[X ≤ x], otherwise, P[X > x], I'm not sure if lower.tail should be set to TRUE or FALSE]
3. For Question #1, it gave me a total of 9 numbers and I'm assuming that they are the probabilities of each number in my range (q= 0:8), but is there a way to get only one probability for this range?? Like one probability that she'll hear <8 calls? 
4. I would like to understand why my bootstrapping attempt using the for loops didn't work. Very frustrating!
5. I don't fully understand the difference between cumulative probabiltiy and probability mass function and how you choose which one you want to look it. 

