---
title: "langley1_OriginalHomeworkCode_02"
output: html_document
---
***

Homework 2: Titis in the Mist

***

This is my code for [Homework 2](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html)
>Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

We want to use the Poisson Distribution because it is often used to model open ended counts of independently occuring events, i.e the number of times a monkey calls in a given interval

The Poisson distribution function, ppois(), returns the value of the cumulative distribution function, i.e., the probability of observing up to and including a specific number of events in the given interval (so this relates to the question)

##Question 1 
What is the probability that she will hear more than 8 calls during any given session?
```{r}
#We know that the mean number of calls is 15, so lambda= 15
#We know that the number of successes should be 8+, so q=8
x<- 0:8
x<- 3
x<- 0

ppois()


```

4) Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
```{r}
x <- 0:30
l = 15
probset<- dpois(x=x,lambda=l)
barplot(probset,names.arg=x,space=0,xlab="x",ylab="Pr(X = x)",main="Probability Mass Function")
```

x<- 0:30
l<- 15

for (i in 1:10000){
    set[i] <- ppois(q=x,lambda=l))
}

